Learning to Group and Order AMR Semantics for General Purpose Discourse Planning

### 2015-12-10 paper/paper.tex

>>>>

\section{Notes on Division of Labor}
At a high level, the task breakdown for the project was:

\noindent Andrew:
\begin{enumerate}
\item AMR parser
\item Generate graph data structures
\item Ordering Module
\item Discrete Optimization
\item Experiments
\end{enumerate}

\noindent Jon:
\begin{enumerate}
\item File parser
\item ARG-of reversal
\item `and'-semantic translation
\item AMR graph merging
\item Subgraph selection module
\end{enumerate}

However, there was significant overlap in many of our tasks. Since we know the division of labor was an issue of concern, we have invited you as a contributor to the github repository. You have full access to our commit history if you wish to further evaluate the individual contributions.
